The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-11-05 script/en/chapters/introduction.tex
CT script: Many small changes; especially referenced CT2, JCT and Sage where previously only CT1 was mentioned.

The later editorial work in TeX added cross linkages between different sections and footnotes describing where you can find the according functions within
the CrypTool programs. The appendices \ref{s:appendix-menu-overview-CT1} etc. contain a complete overview
of\index{CrypTool 1}\index{CrypTool 2}\index{JCrypTool}
the \hyperlink{menu-overview-CT1}{CrypTool 1 menu tree},
the \hyperlink{template-overview-CT2}{CrypTool 2 templates} and
the \hyperlink{function-overview-JCT}{JCrypTool (JCT) functions}.

The rapid spread of the Internet has lead to intensified research in the
technologies involved, especially within the area of cryptography where a good
deal of new knowledge has arisen.

%This edition of the CT script again updated some topics:
This edition completely updated the TeX sources of the document, and of course
the content of the script was amended, corrected, and updated with some topics, e.g.:
\vspace{-5pt}
\begin{itemize}
  \item the definitions of the strength of security functions
        (chap. \ref{cm_Section_Security_Definitions}),
  \item the largest prime numbers (chap. \ref{search_for_very_big_primes}),
        new factorization records (chap. \ref{RSA-768}),
%  \item progress in cryptanalysis of AES 
%        (chap. \ref{NeueAES-Analyse}) and
%  \item progress in cryptanalysis of hash algorithms 
%        (chap. \ref{collision-attacks-against-sha-1}) and
%  \item progress in ideas for new crypto methods (RSA successor) 
%        (chap. \ref{xxxxxxxxxBrute-force-gegen-Symmetr})\index{xxxxxxxxxx} and
  \item the list of movies or novels, in which cryptography or number theory 
        played a major role (see appendix \ref{s:appendix-movies});
        and where primes are used as hangers  
        (see curiouses in \ref{HT-Quaint-curious-Primes-usage}),
  \item the overviews of all functions in
        \hyperlink{template-overview-CT2}{for CT2} and
        \hyperlink{function-overview-JCT}{for JCT},
  \item further Sage scripts for cryptography, and the appendix
        \ref{s:appendix-using-sage} about using the computer algebra system
        Sage. Sage becomes more and more the standard open-source CAS system,
        % Nguyen and Massierer (see also chap.~\ref{ec:Sage_Massierer}).
  \item the section about RSA fixed points (see \ref{l:NumberTheory_Sage_Number-of-RSA-FixedPoints}), and
%  \item the chapter about homomorphic encryption.
\end{itemize}

@@

@@

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\\
\\
% [1.5\baselineskip]
% \enlargethispage*{2\baselineskip}
% \nopagebreak
Bernhard Esslinger
\\
\\
% [\baselineskip]
Frankfurt (Germany), September 2012

@@

\textbf{This script}

@@

\noindent \textbf{The program CrypTool 1\index{CrypTool}}

CrypTool 1 (CT1) is an educational program with a comprehensive
online help enabling you to use and analyse cryptographic procedures within a
unified graphical user interface.

@@

@@

At this point I'd like to thank explicitly the following people who
particularly contributed to CrypTool\index{CrypTool}. They applied their
very special talents and showed really great engagement:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Hr.\ Dominik Schadow
   \item Staff of Prof.\ Claudia Eckert, Prof.\ Johannes Buchmann,
         Prof.\ Torben Weis and Prof.\ Arno Wacker.
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\
\\
Bernhard Esslinger
\\
\\
Frankfurt (Germany), July 2012

>>>>

The later editorial work in TeX added footnotes and cross linkages between
different sections.

%This edition of the CT script again updated some topics:
This edition completely updated the TeX sources of the document, and of course
the content of the script was amended, corrected, and updated with some topics, e.g.:
\vspace{-5pt}
\begin{itemize}
  \item the definitions of the strength of security functions
        (chap. \ref{cm_Section_Security_Definitions}),
%  \item the largest prime numbers (chap. \ref{search_for_very_big_primes}),
%        new factorization records (chap. \ref{RSA-768}),
%  \item progress in cryptanalysis of AES 
%        (chap. \ref{NeueAES-Analyse}) and
%  \item progress in cryptanalysis of hash algorithms 
%        (chap. \ref{collision-attacks-against-sha-1}) and
%  \item progress in ideas for new crypto methods (RSA successor) 
%        (chap. \ref{xxxxxxxxxBrute-force-gegen-Symmetr})\index{xxxxxxxxxx} and
  \item the list of movies or novels, in which cryptography or number theory 
        played a major role (see appendix \ref{s:appendix-movies});
        and where primes are used as hangers  
        (see curiouses in \ref{HT-Quaint-curious-Primes-usage}),
  \item the overviews of all functions in
        \hyperlink{appendix-template-overview-CT2}{for CT2} and
        \hyperlink{appendix-function-overview-JCT}{for JCT},
  \item further Sage scripts for cryptography, and the appendix
        \ref{s:appendix-using-sage} about using the computer algebra system
        Sage. Sage becomes more and more the standard open-source CAS system,
        % Nguyen and Massierer (see also chap.~\ref{ec:Sage_Massierer}).
  \item the section about the Goldbach conjecture
        (see \ref{L-GoldbachConjecture}),
  \item the section about shared primes in RSA modules used in reality
        (see \ref{l:NumberTheory_Shared-Primesxxx}),xxxxxxxxxxxxxxxxxxxx
  \item the section about RSA fixed points
        (see \ref{l:NumberTheory_Sage_Number-of-RSA-FixedPoints}), and
  \item the chapter about homomorphic encryption (see \ref{Chapter_HomomorphicEnc}).
\end{itemize}

@@

In the meantime the CT project gets feedback and testimonials from almost all
countries of the planet.

@@

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\\
\\
Bernhard Esslinger
\\
\\
Frankfurt and Siegen (Germany), October 2012

@@

\textbf{This CrypTool script}

@@

\noindent \textbf{The programs CrypTool 1\index{CrypTool},
  CrypTool 2\index{CrypTool 2} and JCrypTool\index{JCrypTool}}

CrypTool 1 (CT1) is an educational program with a comprehensive
online help enabling you to use and analyse cryptographic procedures within a
unified graphical user interface. The online help in CrypTool 1 contains both
instructions how to use the program and explanations about the methods itself
(both not as detailled and in another structure than the CT script).

@@

\noindent \textbf{CrypTool-Online and MTC3\index{CTO}\index{MTC3}}

Also part of the CT project is the website CrypTool-Online (CTO)
(\url{http://www.cryptool-online.org}), where you can check and apply cryptographic
methods within a browser or on a smartphone. The scope of CTO is far below from
the standalone programs CT1, CT2 and JCT.

Also based on the CT project is the international cryptography contest
MysteryTwister C3 (MTC3) (\url{http://www.mysterytwisterc3.org}).
Here you can find cryptographic riddles in four categories, a
high-score list and a moderated forum. In the meantime more than 3300 active
users participate, and more than 140 challenges are offered (currently 89 of
them are solved by at least one user).
\par \vskip + 15pt

\noindent \textbf{The Computer Algebra System Sage\index{Sage}}

Sage is an open source CAS package which can be used to easily program
the mathematical methods explained in this script.
\par \vskip + 15pt

@@

At this point I'd like to thank explicitly the following people who
particularly contributed to the CrypTool projct\index{CrypTool}. They
applied their very special talents and showed really great engagement:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Hr.\ Dominik Schadow
   \item Staff of 
         Prof.\ Johannes Buchmann,
         Prof.\ Claudia Eckert,
         Prof.\ Alexander May,
         Prof.\ Torben Weis and
         Prof.\ Arno Wacker.
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\
\\
Bernhard Esslinger
\\
\\
Frankfurt and Siegen (Germany), October 2012
\par \vskip + 15pt

\noindent PS:\\
We'd be glad if further authors would show up to add further chapters, e.g. about
hash functions, random numbers or the design and attack of crypto protocols (like SSL).

### 2012-11-05 script/en/chapters/menus.tex
CT script: Many small changes; especially referenced CT2, JCT and Sage where previously only CT1 was mentioned.

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  Since 2010, changes for the stable CrypTool 1 (CT1)\index{CrypTool 1}
  focus mainly on bugfixes. All new developments go into the two successor
  versions CrypTool 2 (CT2)\index{CrypTool 2} and
  JCrypTool (JCT)\index{JCrypTool}:\\
  - Web site CT2: \url{http://www.cryptool.org/en/ct2-documentation-en} \\
  - Web site JCT: \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  These successor versions are currently (July 2012) still beta versions;
  but they are close to their first release and they are already stable
  enough to be used by end-users.\\
}.

@@

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rahmen (siehe viewport) drumherum -- gut zum Testen
%\includegraphics[scale=0.25, angle=270, viewport=200 30 2660 1430]
\includegraphics[scale=0.35, angle=270]
                {figures/CT1-menutree-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\hypertarget{menu-overview-CT1}{}
\caption{Complete overview of the menu tree of CT1 (CrypTool 1.4.31)} 
\label{menu-overview-CT1}
\end{center}
\end{figure}
\clearpage

\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-template-overview-CT2}{}
\section{CrypTool 2 Templates}
\label{s:appendix-template-overview-CT2}

@@

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=270]
                {figures/CT2-templatetree-en-1}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the template tree of CT2 (NB4882.1, July 2012), Part 1} 
\label{template-overview-CT2}
\end{center}
\end{figure}
\clearpage

\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-function-overview-JCT}{}
\section{JCrypTool Functions}
\label{s:appendix-function-overview-JCT}

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-EN}
\hypertarget{welcome-JCT}{}
\caption{Welcome screenshot in JCT (RC6, July 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
After pressing ``Start'' you can directly use the different functions.
The functions implemented in JCT are presented in two different perspectives:
\begin{itemize}
   \item Default Perspective
   \item Funktional Perspective
 \end{itemize}

@@

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 1} 
\label{functions-overview-1-JCT}
\end{center}
\end{figure}
\clearpage

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-2}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 2} 
\label{functions-overview-2-JCT}
\end{center}
\end{figure}
\clearpage

>>>>

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  Since 2010, changes for the stable CrypTool 1 ({\bf CT1})\index{CrypTool 1}
  focus mainly on bugfixes. Many new developments go into the two successor
  versions CrypTool 2 ({\bf CT2})\index{CrypTool 2} and
  JCrypTool ({\bf JCT})\index{JCrypTool}:\\
  - Web site CT2: \url{http://www.cryptool.org/en/ct2-documentation-en} \\
  - Web site JCT: \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  These successor versions are currently (Nov. 2012) still beta versions;
  but they are close to their first release and they are stable enough
  since quite a while to be used by end-users.\\
}.

@@

%--------------------------------------------------------------------
%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rahmen (siehe viewport) drumherum -- gut zum Testen
%\includegraphics[scale=0.25, angle=270, viewport=200 30 2660 1430]
\includegraphics[scale=0.35, angle=270]
                {figures/CT1-menutree-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\hypertarget{appendix-figure-menu-overview-CT1}{}
\caption{Complete overview of the menu tree of CT1 (CrypTool 1.4.31)} 
\label{appendix-figure-menu-overview-CT1}
\end{center}
\end{figure}
\clearpage

%--------------------------------------------------------------------
\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-template-overview-CT2}{}
\section{CrypTool 2 Templates}
\label{s:appendix-template-overview-CT2}

@@

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=270]
                {figures/CT2-templatetree-en-1}
\hypertarget{appendix-figure-template-overview-CT2}{}
\caption{Screenshot of the template tree of CT2 (NB4882.1, July 2012), Part 1} 
\label{appendix-figure-template-overview-CT2}
\end{center}
\end{figure}
\clearpage

%--------------------------------------------------------------------
\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-function-overview-JCT}{}
\section{JCrypTool Functions}
\label{s:appendix-function-overview-JCT}

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-EN}
\hypertarget{Welcome-Screenshot-JCT}{}
\caption{Welcome screenshot in JCT (RC6, July 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
After pressing ``Start'' you can directly use the different functions.
The functions implemented in JCT are presented in two different perspectives:
\begin{itemize}
   \item Default Perspective
   \item Funktional Perspective
 \end{itemize}

@@

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{functions-overview-1-JCT}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 1} 
\label{functions-overview-1-JCT}
\end{center}
\end{figure}
\clearpage

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-2}
\hypertarget{functions-overview-2-JCT}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 2} 
\label{functions-overview-2-JCT}
\end{center}
\end{figure}
\clearpage

%--------------------------------------------------------------------
\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-function-overview-CTO}{}
\section{CrypTool-Online Functions}
\label{s:appendix-function-overview-CTO}

\noindent This appendix contains a list of all
functions in CrypTool-Online (CTO)\index{CrypTool-Online}.\footnote{%
  You can find further information about CTO at:
  \url{www.cryptool-online.org} \\
  This list was generated using the functions list at the CT Portal website:\\
  \url{http://www.cryptool.org/ctp-documentation-en/ctp-functions-en}}

%\noindent The starting page of CTO looks like this:
%\begin{figure}[hb]
%\begin{center}
%\vspace{-30pt}
%\includegraphics[scale=0.45, angle=0] {figures/CTO-Welcome-EN}
%\hypertarget{Welcome-Screenshot-CTO}{}
%\caption{Welcome screenshot in CrypTool-Online (November 2012)} 
%\label{Welcome-Screenshot-CTO}
%\end{center}
%\end{figure}

\noindent The following screenshot shows the crypto functions implemented on CTO:
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{functions-overview-1-CTO}{}
\caption{Screenshot of the functions of CTO (November 2012)} 
\label{functions-overview-1-JCT}
\end{center}
\end{figure}
\clearpage

%\clearpage
%\begin{figure}[hb]
%\begin{center}
%\vspace{-30pt}
%\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-2}
%\hypertarget{functions-overview-2-CTO}{}
%\caption{Screenshot of the functions of CTO (November 2012), Part 2} 
%\label{functions-overview-2-CTO}
%\end{center}
%\end{figure}
%\clearpage

### 2012-11-05 script/en/chapters/moderncryptography.tex
CT script: Many small changes; especially referenced CT2, JCT and Sage where previously only CT1 was mentioned.

\vskip +30 pt

\begin{center}
\fbox{\parbox{15cm}{
   {\em Georg Christoph Lichtenberg\footnotemark:}\\
   I don't know if its getting better, if we change it,\\
   but I know, that we have to change it, if it should become better.
}}
\end{center}
\addtocounter{footnote}{0}\footnotetext{%
  Georg Christoph Lichtenberg\index{Lichtenberg, Georg Christoph}, 
  German writer and physicist (1742-1799),\\ 
  (also see: \href{http://en.wikipedia.org/wiki/Georg\_Christoph\_Lichtenberg}
              {\tt http://en.wikipedia.org/wiki/Georg\_Christoph\_Lichtenberg})
}

>>>>

%\vskip +30 pt
\begin{ctsquote}
   I don't know if its getting better, if we change it,\\
   but I know, that we have to change it, if it should become better.%TODO - Rest von German
\caption[Georg Christoph Lichtenberg]{Georg Christoph Lichtenberg\footnotemark}
\end{ctsquote}
\footnotetext{%
  Georg Christoph Lichtenberg\index{Lichtenberg, Georg Christoph}, 
  German writer and physicist (1742-1799),\\ 
  (also see: \href{http://en.wikipedia.org/wiki/Georg\_Christoph\_Lichtenberg}
              {\tt http://en.wikipedia.org/wiki/Georg\_Christoph\_Lichtenberg})
}

### 2012-11-05 script/en/chapters/numbertheory.tex
CT script: Many small changes; especially referenced CT2, JCT and Sage where previously only CT1 was mentioned.

\vskip +40 pt

\begin{center}
\fbox{\parbox{15cm}{{\em Carl Friedrich Gauss\index{Gauss, Carl Friedrich}:}\\
Mathematics is the queen of sciences and number theory is the queen of
mathematics.}}
\end{center}

@@

\begin{center}
\fbox{\parbox{15cm}{{\em Joanne\index{Rowling,
Joanne} K. Rowling\footnotemark\:}\newline This isn't 
magic -- it's logic -- a puzzle. A lot of the greatest 
wizards haven't got an ounce of logic.}}
\end{center}

\addtocounter{footnote}{0}\footnotetext{Joanne K. Rowling,~``Harry Potter and the Philosopher's Stone'', Bloomsbury, (c) 
1997, chapter ``Through the trapdoor'', p. 307, by Hermine.}

@@

\newpage
\begin{center}
\fbox{\parbox{15cm}{
    \emph{Seneca\index{Seneca}\footnotemark:}\\
    The way of theory is long  ---  it is short and effective by examples.
}}
\end{center}
\addtocounter{footnote}{0}
\footnotetext{%
     Lucius Annaeus Seneca, philosophical writer and poet, 4 B.\:C. $-$ 65 A.\:D.}

@@

% --------------------------------------------------------------------------
\pagebreak
\begin{center}
\fbox{\parbox{15cm}{{\em Eric Berne\footnotemark:\index{Berne, Eric}}\newline
Mathematical game theory postulates players who respond rationally.
Transactional game theory, on the other hand, deals with games that are 
not rational, perhaps even {\bf irrational and thereby closer to reality}.}}
\end{center}
\addtocounter{footnote}{0}\footnotetext{Eric Berne, ``Games People Play'', 
     rororo, (c) 1964, page 235.}
\vskip +4pt

@@

\clearpage
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\vspace{4ex}
\begin{center}
\fbox{\parbox{15cm}{
    \emph{Hermann Hesse\footnotemark:}\\
    To let the possible happen, you again and again have to try the impossible.
}}
\end{center}
\addtocounter{footnote}{0}\footnotetext{%
  Hermann Hesse, German/Swiss writer and Nobel Prize winner, July 2, 1877 $-$ August 9, 1962.\\}
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
% \vskip +40 pt
\newpage
\begin{center}
\fbox{\parbox{15cm}{{\em Joanne\index{Rowling, Joanne} K. Rowling\footnotemark:}\\
It is our choices, that show what we truly are, far more than our abilities.}}
\end{center}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{Chapter_ElementaryNT_12}{}
\section[The RSA procedure with actual numbers]{The RSA procedure with actual numbers\footnotemark}
\footnotetext{%
    \index{Sage}%
    \index{Nguyen, Minh Van }%
    Additional material: Minh Van Nguyen, ``Number Theory and the RSA
    Public Key Cryptosystem'', 2009. An introductory tutorial on using
    Sage to study elementary number theory and public key
    cryptography. A didactically very clear article about some basic
    number theory and Sage usage. 
    \url{http://nguyenminh2.googlepages.com/sage_numtheory-rsa.pdf}.
}
\label{rsaconcrete}\index{RSA}
Having described above \hyperlink{RSA}{how the RSA procedure works}, we will now work through the steps using actual, but small, numbers.

@@

\noindent Below is Sage source code related to contents of the
chapter~\ref{Chapter_ElementaryNT} (``\nameref{Chapter_ElementaryNT}'').

>>>>

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{ctsquote}
Mathematics is the queen of sciences and number theory is the queen of
mathematics.
\caption{Carl Friedrich Gauss}\index{Gauss, Carl Friedrich}
\end{ctsquote}

@@

\begin{ctsquote}
This isn't magic -- it's logic -- a puzzle.
A lot of the greatest wizards haven't got an ounce of logic.
\caption[Joanne K. Rowling]{Joanne K. Rowling\footnotemark}\index{Rowling, Joanne}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Joanne K. Rowling,~``Harry Potter and the Philosopher's Stone'', Bloomsbury, (c) 
1997, chapter ``Through the trapdoor'', p. 307, by Hermine.}

@@

\newpage
\begin{ctsquote}
    The way of theory is long  ---  it is short and effective by examples.
\caption[Seneca]{Seneca\footnotemark}\index{Seneca}
\end{ctsquote}
\addtocounter{footnote}{0}
\footnotetext{%
     Lucius Annaeus Seneca, philosophical writer and poet, 4 B.\:C. $-$ 65 A.\:D.}

@@

% --------------------------------------------------------------------------
\pagebreak
\begin{ctsquote}
Mathematical game theory postulates players who respond rationally.
Transactional game theory, on the other hand, deals with games that are 
not rational, perhaps even {\bf irrational and thereby closer to reality}.
\caption[Eric Berne]{Eric Berne\footnotemark}\index{Berne, Eric}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Eric Berne, ``Games People Play'', 
     rororo, (c) 1964, page 235.}
\vskip +4pt

@@

\clearpage
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\vspace{4ex}
\begin{ctsquote}
    To let the possible happen, you again and again have to try the impossible.
\caption[Hermann Hesse]{Hermann Hesse\footnotemark}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{%
  Hermann Hesse, German/Swiss writer and Nobel Prize winner, July 2, 1877 $-$ August 9, 1962.\\}
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
% \vskip +40 pt
\newpage
\begin{ctsquote}
It is our choices, that show what we truly are, far more than our abilities.
\caption[Joanne K. Rowling]{Joanne K. Rowling\footnotemark}\index{Rowling, Joanne}
\end{ctsquote}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{Chapter_ElementaryNT_12}{}
\section[The RSA procedure with actual numbers]{The RSA procedure with actual numbers\footnotemark}
\footnotetext{%
    \index{Sage}%
    \index{Nguyen, Minh Van }%
    Additional material: Minh Van Nguyen, ``Number Theory and the RSA
    Public Key Cryptosystem'', 2009. An introductory tutorial on using
    Sage to study elementary number theory and public key
    cryptography. A didactically very clear article about some basic
    number theory and Sage usage. 
    \url{http://nguyenminh2.googlepages.com/sage_numtheory-rsa.pdf}.
}
\label{rsaconcrete}\index{RSA}

\begin{ctsquote}
``Games are Nature's way of preparing us to face difficult realities. Are you finally ready to face reality, Sergeant?''
\caption[Daniel Suarez, Daemon]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Daemon'', Dutton Adult, 2010,
Chapter 45, ``Respawning'', p. 610, Sobol.}

Having described above \hyperlink{RSA}{how the RSA procedure works}, we will now work through the steps using actual, but small, numbers.

@@

\begin{ctsquote}
``She would never be able to tell her parents ... about any of this. She couldn't tell them about her code-breaking work. About her near death at the hands of the Daemon. About the shadowy entities pulling the strings of her government.''
\caption[Daniel Suarez, Freedom]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Freedom'', Dutton Adult, 2010,
                          Chapter 5, ``Crossroad'', p. 229, Philips.}

\noindent Below you can find Sage source code related to contents of the
chapter~\ref{Chapter_ElementaryNT} (``\nameref{Chapter_ElementaryNT}'').
